HealpixNet: Efficient spherical Convolutional Neural Network with HEALPix sampling for cosmological applications

### 2018-08-28 scnn.tex
crop figures

\begin{figure*}
	\centering
    % \includegraphics[width=\linewidth]{architecture}
	\includegraphics[width=\linewidth]{figure_architecture_v3.pdf}
	\caption{Overall network architecture, showing here two convolutional layers acting as feature extractors followed by a fully connected layer with softmax acting as the classifier.
    %\nati{add the stat layer?}
    %\TK{added stats layer to figure text, hope that's OK}
    A convolutional layer is based on five operations: convolution, non-linearity, batch normalization, down-sampling, and pooling. While most operations are agnostic to the data domain, the convolution and the down-sampling have to be adapted. In this paper, we propose first to model the sphere with a graph and to perform the convolution on the graph. Graphs are versatile data structures which can model any sampling, even irregular or partial. Second, we propose to exploit a hierarchical pixelization of the sphere for the pooling operation. It allows the network to analyze the data at multiple scales while preserving the spatial localization of features. This figure shows a network which operates on the whole sphere. The process is, however, the same when working with parts of sphere, except that the graph is only built for the part of interest.}
	\label{fig:architecture}
\end{figure*}

@@

\begin{figure*}
\includegraphics[width=\linewidth]{figures/figure_example_maps.pdf}
\caption{Exmaple maps on the sphere:
(left) the CMB temperature (K) map from Planck \citep{planck2015overview}, with galactic plane masked,
(middle) map of galaxy number counts (number of galaxies per arcmin$^2$) in SDSS DR14 \citep{abolfathi2017sdssDR14},
and (right) simulated weak lensing convergence map (dimensionless) simulated with DES DR1 mask \citep{des2018dr1}.
These maps were pixelised using $N_{side} = 512$.
The CMB and weak lensing mass maps were smoothed with Gaussian kernels with FWHM=1 deg, and the galaxy count map with FWHM=0.5 deg.
}
\label{fig:example_maps}
\end{figure*}

@@

\begin{figure}
	\centering
    % \includegraphics[width=\linewidth]{pooling}
	\includegraphics[trim=1.1cm 0cm 0cm 0cm, width=\linewidth]{figures/figure_pooling_svg.pdf}
	\caption{Two levels of coarsening and pooling: groups of 4 cells are merged into one, then the data on them is summarized in one. The coarsest cell covers $1/12$ of the sphere.}
	\label{fig:pooling}
\end{figure}

@@

\begin{figure*}
	\centering
	% \includegraphics[width=0.75\linewidth]{smooth_map_class_1}
	% trim=left bottom right top
	\includegraphics[trim=1cm 0cm 0cm 0cm, width=0.49\linewidth]{figure_kappa_diff_model1.pdf}
	\hfill
	% \includegraphics[width=0.75\linewidth]{smooth_map_class_2}
	\includegraphics[trim=0cm 0cm 1cm 0cm, width=0.49\linewidth]{figure_kappa_diff_model2.pdf}
	\caption{Example maps from two classes to be discriminated. Left: model 1 with $\Omega_m=0.31$ and $\sigma_8=0.82$. Right: model 2 with $\Omega_m=0.26$ and $\sigma_8=0.91$.
	The initial conditions for both simulations are the same, so differences only arise due to different cosmological parameters.}
	\label{fig:map_sample}
\end{figure*}

>>>>

\begin{figure*}
	\centering
    % \includegraphics[width=\linewidth]{architecture}
	\includegraphics[width=\linewidth]{figure_architecture_v3}
	\caption{Overall network architecture, showing here two convolutional layers acting as feature extractors followed by a fully connected layer with softmax acting as the classifier.
    %\nati{add the stat layer?}
    %\TK{added stats layer to figure text, hope that's OK}
    A convolutional layer is based on five operations: convolution, non-linearity, batch normalization, down-sampling, and pooling. While most operations are agnostic to the data domain, the convolution and the down-sampling have to be adapted. In this paper, we propose first to model the sphere with a graph and to perform the convolution on the graph. Graphs are versatile data structures which can model any sampling, even irregular or partial. Second, we propose to exploit a hierarchical pixelization of the sphere for the pooling operation. It allows the network to analyze the data at multiple scales while preserving the spatial localization of features. This figure shows a network which operates on the whole sphere. The process is, however, the same when working with parts of sphere, except that the graph is only built for the part of interest.}
	\label{fig:architecture}
\end{figure*}

@@

\begin{figure}
\includegraphics[width=\linewidth]{figure_example_maps}
\caption{Example maps on the sphere:
(left) the CMB temperature (K) map from Planck \citep{planck2015overview}, with galactic plane masked,
(middle) map of galaxy number counts (number of galaxies per arcmin$^2$) in SDSS DR14 \citep{abolfathi2017sdssDR14},
and (right) simulated weak lensing convergence map (dimensionless) simulated with DES DR1 mask \citep{des2018dr1}.
These maps were pixelised using $N_{side} = 512$.
The CMB and weak lensing mass maps were smoothed with Gaussian kernels with FWHM=1 deg, and the galaxy count map with FWHM=0.5 deg.
}
\label{fig:example_maps}
\end{figure}

@@

\begin{figure}
	\centering
    % \includegraphics[width=\linewidth]{pooling}
	\includegraphics[width=\linewidth]{figure_pooling_svg}
	\caption{Two levels of coarsening and pooling: groups of 4 cells are merged into one, then the data on them is summarized in one. The coarsest cell covers $1/12$ of the sphere.}
	\label{fig:pooling}
\end{figure}

@@

\begin{figure*}
	\centering
	% \includegraphics[width=0.75\linewidth]{smooth_map_class_1}
	% trim=left bottom right top
	\includegraphics[width=0.48\linewidth]{figure_kappa_diff_model1}
	\hfill
	% \includegraphics[width=0.75\linewidth]{smooth_map_class_2}
	\includegraphics[width=0.48\linewidth]{figure_kappa_diff_model2}
	\caption{Example maps from two classes to be discriminated. Left: model 1 with $\Omega_m=0.31$ and $\sigma_8=0.82$. Right: model 2 with $\Omega_m=0.26$ and $\sigma_8=0.91$.
	The initial conditions for both simulations are the same, so differences only arise due to different cosmological parameters.}
	\label{fig:map_sample}
\end{figure*}
